\section{Background}
In todays society more and more information is shared through internet.
A lot of the communication consist of sharing pictures, stories and information with friends and family.
The online websites that allow and promote these services are often very easy to use and especially easy to register a new account for.
To log in to most of these services the required credentials are often username and password. 
%which is deemed as a low assurance level \cite[p.~244]{pdf:SOU}.
%This has its pros and cons, though in the end, the above mentioned services might not need higher assurance level.

Services that require somekind of proof that the user behind the keyboard really is the person he/she says he/she is, are lagging behind in the online era.
A solution to this problem is "BankID" which was introduced in 2003 \cite{website:bankid-about} in Sweden.
Other solutions comes from Nordea, SEB, Telia, Posten and Steria \cite[p.~256]{pdf:SOU}.
All listed solutions have their pros and cons and a new solution is in the horizon.
A new solution is being built upon the concept of identity federations \cite[p.~23]{pdf:SOU}, \cite{website:elegnamnd}.

One major identity federation that exists in Sweden today is SWAMID, it's for students in higher education and is run by SUNET.
Another one is "Skolfederation.se" which is planned to go into production during 2013.
"Skolfederation.se" is for pupils/parents and teachers in compulsary primary and secondary school run by .SE and SUNET. 
Other federations that soon will come in to production is "E-legitimationsn{\"a}mden" \cite{website:elegnamnd} and "V\r{a}rd, h{\"a}lsa, omsorg" according to .SE.  

An identity federation does not have the goal to increase security and therefore will probably continue to use the same authentication mechanism that has been used before e.g. username and password. 
However, the federation provides user friendliness since the user only has to have one username and one password to all services within the federation. 

%As of today two major identity federations exists in Sweden.
%Those are SWAMID for students in higher education run by SUNET and "Skolfederation.se" for pupils/parents and teachers in compulsary primary and secondary school run by .SE and SUNET. "Skolfederation.se" is planned to go into production during 2013.


%In our thesis we dig deeper into the identity federation and examine how DNS-Based Authentication of Named Entities (DANE) 
%\cite{rfc:6394,rfc:draft-dane,rfc:draft-smime} can be used to improve the security in identity federations.

\section{Problem area}
%The subject of the thesis is divided into smaller subsections. 
The work of the thesis is divided into the following questions:
\\\\
%- An analysis of the security mechanism used to achieve data integrity in an identity federation and specifically the use of X.509 certificates.
1. In an identity federation and specifically the use of X.509 certificates,
is it possible to improve the security mechanism used to achive data integrity?
\\\\
%- Two separate evaluations one about the possibility to use DANE to improve the security for an identity federation
%and another one concern the possibility to implement support for DANE in the open source software package Shibboleth.
2. Can DANE be used to improve the security for an identity federation? 
\\\\
3. Is it possible to implement support for DANE in the open source software package Shibboleth? 
\\\\
%- Implementation of DANE in Shibboleth, simpleSAMLphp or equivalent software to improve the security for an identity federation.
4. Implemention of DANE in Shibboleth, simpleSAMLphp or equivalent software to improve the security for an identity federation. Is it possible?
If it is possible, implement.

%Firstly, an analysis of the security mechanism used to achieve data integrity in an identity federation and 
%specifically the use of X.509 certificates.
%Secondly, two separate evaluations one about the possibility to use DANE to improve the security for an identity federation
%and another one concern the possibility to implement support for DANE in the open source software package Shibboleth.
%Finally, the implementation of DANE in Shibboleth, simpleSAMLphp or equivalent software to improve
%the security for an identity federation.

\section{Purpose}
The purpose with this thesis is to show that DNS-Based Authentication of Named Entities (DANE) \cite{rfc:6394,rfc:draft-dane,rfc:draft-smime} can be used to improve security for identity federations.
In the same time proving DNS Security Extension (DNSSEC) \cite{rfc:4033,rfc:4034,rfc:4035,rfc:5011} useful, since DANE is 
depending on the use of DNSSEC.

\section{Project delimitations}
As stated above this project will be about DANE and identity federations and as with most, if not all implementation of different protocols and standards, a lot of underlying technology is used.
This is also the case with DANE and identity federations.

Within an identity federation there are four main entities which are clients, service providers, identity providers and in most cases a federation operator.
All entities might communicate with each other over different protocols and communication schemes.
In this project the main focus has been on communication over HTTPS.

A firm delimitation in this report is that of excluding how Transport Layer Security (TLS) and Secure Sockets Layer (SSL) works in detail and why it's deemed as a secure way for transmission between two hosts.
Some parts in the report will touch the topic of the TLS/SSL handshaking process but will not go into further detail.
The focus in this report is on the actual data that is being transmitted (SAML2 requests and responses) and how it's deemed secure. 

Another delimitation is made concerning DANE, DNS and DNSSEC.
DANE uses DNSSEC and DNS as an underlying technology and security schemes/protocols.
As the focus is on DANE, issues that might exist with DNS and DNSSEC in general is not discussed in this report.


%The other main part in this report is the one concerning DANE, DNS and DNSSEC.
%DANE uses DNSSEC and DNS as an underlying technology and security schemes/protocols.
%As the focus is on DANE, issues that might exist with DNS and DNSSEC in general is not discussed in this report.

%---
%INTRODUCTION 

%Background: A short background, the reason why the work was carried out, and why you chose that particular topic.

%Problem description: Problem area A broader discussion of what you are going to write about (the task). This can often be included under the same heading as the introduction. Formulating the problem leads to the purpose.

%Purpose: The purpose may for example be specified in a list of to clauses.

%Project delimitation: Arguments and boundaries. You must naturally give the reasons for your delimitations.
